Models of lens candidates from Space Warps CFHTLS

### 2016-12-12 paper2.tex
edits

\edef\smallwidth{0.4\linewidth}

\newcommand{\inclfig}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
%	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
        \includegraphics[width=\smallwidth]{img/arrival_spaghetti/#1_#2_arrival_spaghetti}%
%        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
}

\newcommand{\inclfign}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
%        \includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
        \includegraphics[width=\smallwidth]{img/arrival_spaghetti/#1_#2_arrival_spaghetti}%
%	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
}

@@

\def\pwidth{.32\linewidth}

\def\includeten#1#2{
\includegraphics[width=\pwidth]{#1ASW0007iwp_4XBJWT3COV#2}%
\includegraphics[width=\pwidth]{#1ASW0007xrs_JHC3J2HYV7#2}%
\includegraphics[width=\pwidth]{#1ASW0008pag_5SXGXQYY6V#2}\\
\includegraphics[width=\pwidth]{#1ASW0007k4r_N7LTELSYTM#2}%
\includegraphics[width=\pwidth]{#1ASW00096rm_4Q3YCEWGLN#2}%
\includegraphics[width=\pwidth]{#1ASW0001ld7_OS3CYAKLRT#2}\\
\includegraphics[width=\pwidth]{#1ASW0002asp_5EKMWWVJHL#2}%
\includegraphics[width=\pwidth]{#1ASW0008qsm_TOFS7JNGEK#2}%
\includegraphics[width=\pwidth]{#1ASW000619d_011489#2}\\
%\includegraphics[width=\pwidth]{#1ASW000096t_7IPP7LWVOF#2}%
}

\def\includezehn#1#2{
\includegraphics[width=\pwidth]{#1SW58_ASW0007iwp_4XBJWT3COV#2}%   L
\includegraphics[width=\pwidth]{#1SW28_ASW0007xrs_JHC3J2HYV7#2}%   L
\includegraphics[width=\pwidth]{#1SW57_ASW0008pag_5SXGXQYY6V#2}\\% X
\includegraphics[width=\pwidth]{#1SW05_ASW0007k4r_N7LTELSYTM#2}%   I
\includegraphics[width=\pwidth]{#1SW42_ASW00096rm_4Q3YCEWGLN#2}%   I
\includegraphics[width=\pwidth]{#1SW19_ASW0001ld7_OS3CYAKLRT#2}\\% I
\includegraphics[width=\pwidth]{#1SW09_ASW0002asp_5EKMWWVJHL#2}%   S
\includegraphics[width=\pwidth]{#1SW29_ASW0008qsm_TOFS7JNGEK#2}%   S
\includegraphics[width=\pwidth]{#1SW02_ASW000619d_011489#2}\\%     S
%\includegraphics[width=\pwidth]{#1SW36_ASW000096t_7IPP7LWVOF#2}%
}

@@

\input parts/spl

@@

>>>>

@@

@@

% \input parts/spl

@@

\input parts/figures

### 2016-12-12 parts/massmodel.tex
figure changes
edits

\section{Mass models}

\begin{figure*}
\includezehn{img/kappa_map/}{_kappa_map}
\caption{\label{fig:kappa}}
\end{figure*}

\begin{figure*}
\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
\caption{\label{fig:arriv}}
\end{figure*}

\begin{figure*}
\includeten{img/nsynth/}{_nsynth}
\label{fig:synth}
\caption{}
\end{figure*}

@@

\begin{figure*}
\includezehn{img/kappa_encl/}{_kappa_encl}
\caption{}
\end{figure*}

>>>>

\section{Mass models}\label{sec:massmodels}

A SpaghettiLens model consists of a statistical ensemble of free-form
maps of the sky-projected mass distribution responsible for lensing.
  Photometric lens
redshifts are used; source redshifts are set to $z=2$ unless an
unambiguous photometric redshift is available.  The models can,
however, be trivially rescaled to use better redshift values, as and
when they become available.

A spaghetti diagram is read by a server-side numerical engine
\citep[GLASS, developed by][]{2014MNRAS.445.2181C} which then returns
a statistical ensemble of mass maps.  The mass maps are made up of
mass tiles and are free-form, except that they are required to be
concentrated around the identified lens centre.  They are also
required to reproduce the given image locations, parities and time
ordering exactly.  Graphical representations of the mass map and
arrival-time surface are returned to the user for review.  The user
can post these results on a forum, or discard them and try again.
Volunteers can start the modelling process afresh, or they can take an
existing model from the forum and modify its input spaghetti diagram
or its accompanying options, and thus obtain a revised model.

@@

### 2016-12-12 parts/morph.tex
figure changes
edits

\section{Image morphology}

@@

The lenses are arranged as follows.
$$
\begin{matrix}
\rm SW05 & \rm SW42 & \rm SW28 \\
\rm SW58 & \rm SW02 & \rm SW19 \\
\rm SW09 & \rm SW29 & \rm SW57
\end{matrix}
$$ 
$\{${\em Panels will be labelled, and this little table removed.}$\}$

@@

\begin{figure*}
\includeten{spaghetti/}{_input}
\caption{Marked-up images. \label{fig:markedup}}
\end{figure*}

>>>>

\section{Image morphology}\label{sec:morph}

A modeller's main input to SpaghettiLens is a sketch of arrival-time
contours on a lensed system.  It gives the locations (or best-guess
locations) of images of point-like sources, along with their ordering
in arrival time, and their parities (minumum, saddle-point or
maximum).  Such a sketch, which we call a spaghetti diagram, tends to
resemble the form of lensed arcs, but it also in effect 
encodes a proposal for its mass distribution.

@@

The lenses are arranged as follows.
$$
\begin{matrix}
\rm SW58 & \rm SW28 & \rm SW57 \\
\rm SW05 & \rm SW42 & \rm SW19 \\
\rm SW09 & \rm SW29 & \rm SW02
\end{matrix}
$$ 
$\{${\em Panels will be labelled, and this little table removed.}$\}$

@@

### 2016-12-12 parts/summary.tex

\section{Summary of models}

Now we give a concise characterisation of each modelled system,
according to the image morphology and how clear or indistinct it is,
whether the mass map and synthetic lensed image appear to be
plausible, and how the model mass compares with the estimated stellar
and full-halo masses.

@@

@@

For SW42 the inferred mass is at the low end of the sample.  (The
synthetic image shown is cruder than for the five previous figures,
but that does not influence the mass models.)  If these preliminary
findings are confirmed by follow-up observations, this could be the
most dark-matter dominated lens known.\todo{Check photometry of this
  candidate.}

>>>>

\section{Summary of models}\label{sec:summary}

@@

Accordingly the the characterisation of each modelled system is
(i)~according to the image morphology and how clear or indistinct it
is, (ii)~whether the mass map and synthetic lensed image appear to be
plausible, and (iii)~how the model mass compares with the estimated
stellar and full-halo masses.

@@

For SW42 the inferred mass is at the low end of the sample.  (The
synthetic image shown is cruder than for the five previous figures,
but that does not influence the mass models.)  If these preliminary
findings are confirmed by follow-up observations, this could be the
most dark-matter dominated lens known.
